### 2016-05-20 cv-body.tex
Update CV

@@

Monnahan, C.C., K. Ono, S.C Anderson, M.B. Rudd, A.C. Hicks, F.
Hurtado-Ferro, K.F. Johnson, P.T. Kuriyama, R.R. Licandeo, C.C. Stawitz,
I.G. Taylor, J.L. Valero. The effect of length bin width on growth
estimation in integrated age-structured stock assessments. In press.

@@

Kuriyamaa, P.T., F. Hurtado-Ferro, K. Ono, A.C. Hicks, I.G. Taylor, R.R.
Licandeo, K.F. Johnson, S.C. Anderson, C.C. Monnahan, M.B. Rudd, C.C.
Stawitz, J.L. Valero. An empirical weight-at-age approach reduces
estimation bias compared to modeling parametric growth in integrated,
statistical stock assessment models when growth is time varying. In
press. \url{http://doi.org/10.1016/j.fishres.2015.11.002}

@@

Finnegan*, S., \textbf{S.C. Anderson}*, P.G. Harnik*, C. Simpson, D.P.

@@

Lockwood, H.K. Lotze, C.M. McClain, J.L. McGuire, A. O'Dea, J.M.

@@

(\href{https://github.com/seananderson/paleobaselines}{GitHub
repository}) (\emph{*Authors contributed equally}).
Orzechowski, E.A., R. Lockwood, J.E. Byrnes, \textbf{S.C. Anderson}, S.
Finnegan, Z.V. Finkel, P.G. Harnik, D.R. Lindberg, L.H. Liow, H.K.
interactions over 500 million years. In press at Global Change Biology.
of Animal Ecology. 83(3):840--850.
\url{http://doi.org/10.1111/1365-2656.12322}.
(\href{https://github.com/seananderson/lobsters-predators}{GitHub
repository})

@@

Marine Science. 72(1): 99--110.
\url{http://doi.org/10.1093/icesjms/fsu198}.
Ecological Applications. 2015. 25(2): 559--572.
(\href{https://dl.dropboxusercontent.com/u/254940/papers/Anderson_etal_2014_salmon_portfolios.pdf}{PDF},
\href{https://github.com/seananderson/metafolio}{GitHub repository},
\href{http://cran.r-project.org/web/packages/metafolio/index.html}{CRAN
R package}).
(\href{http://icesjms.oxfordjournals.org/content/early/2014/04/09/icesjms.fsu055.full.pdf?keytype=ref\&ijkey=NEXmZIkz3289u3z}{PDF},
\href{https://github.com/ss3sim/natural-mortality}{GitHub repository}).
Monnahan, C.S. Szuwalski, J.L. Valero, K.A. Vert-pre, A.R. Whitten, A.E.
catch-at-age models for marine species. ICES Journal of Marine Science.
72(1): 31--43. \url{http://doi.org/10.1093/icesjms/fsu007}
(\href{https://dl.dropboxusercontent.com/u/254940/papers/Ono_etal_2014_importance_of_length_and_age_composition_data.pdf}{PDF}).

@@

@@

\begin{description}
\itemsep3pt\parskip0pt\parsep0pt
\item[2013]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
challenges of quantifying ecological portfolios
(\href{http://seananderson.ca/talks/2013/PE_SAFS_quantsem.pdf}{slides}),
Quantitative Seminar, School of Aquatic and Fishery Sciences, University
of Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
ecological portfolio effect overestimates the benefit of diversity.
Branch Lab, School of Aquatic and Fishery Sciences, University of
Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. Metapopulation
dynamics and the generality of the ecological portfolio effect. Les
Ecologistes Departmental Seminar, Simon Fraser University, Burnaby, BC,
Canada.
\item[2010]
\textbf{Anderson, S.C.} The rise of invertebrates, the fall of sea
cucumbers, and the risk of maturing late. Earth2Ocean Research Group,
Simon Fraser University, Burnaby, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E. Mills Flemming, R. Watson, H.K. Lotze.
Ecosystem impacts of the global expansion of invertebrate fisheries.
International Oceans Past II Conference \emph{Multidisciplinary
Perspectives on the History and Future of Marine Animal Populations}.
Vancouver, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E Mills Flemming, R. Watson, H.K. Lotze.
Global invertebrate fisheries: trends and consequences. NCEAS (National
Center for Ecological Analysis and Synthesis) Working Group
\emph{Finding Common Ground in Marine Conservation and Management}.
Santa Barbara, CA, USA.
\item[2009]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Harvest Fisheries Seminar Series. Bedford Institute of
Oceanography, Fisheries and Oceans, Dartmouth, NS, Canada.
\item[2008]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Departmental Seminar, Biology Department, Dalhousie University,
Canada.
\end{description}

@@

Reviewer for Science, Ecology, Conservation Biology, Fish and Fisheries,
International Journal of Tropical Biology and Conservation, Journal of
Environmental Management, Endangered Species Research, Aquatic
Conservation

>>>>

\item[2016]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities.
Proceedings of the Royal Society B: Biological Sciences. In press.
\item[2016]
Artelle, K.A., \textbf{S.C. Anderson}, J.D. Reynolds, A.B. Cooper, P.C.
Paquet, C.T. Darimont. Ecology of conflict: marine food supply affects
human-wildlife interactions on land. Scientific Reports. 6: 25936.
\url{http://doi.org/10.1038/srep25936}
(\href{http://www.nature.com/articles/srep25936.pdf}{PDF}).
\item[2016]
Kuriyama, P.T., K. Ono, F. Hurtado-Ferro, A.C. Hicks, I.G. Taylor, R.R.
Licandeo, K.F. Johnson, \textbf{S.C. Anderson}, C.C. Monnahan, M.B.
Rudd, C.C. Stawitz, J.L. Valero. An empirical weight-at-age approach
reduces estimation bias compared to modeling parametric growth in
integrated, statistical stock assessment models when growth is time
varying. Fisheries Research. 180: 119--127.
(\href{https://dl.dropboxusercontent.com/u/254940/papers/Kuriyama_etal_2016_empirical.pdf}{PDF}).
\item[2016]
Monnahan, C.C., K. Ono, \textbf{S.C. Anderson}, M.B. Rudd, A.C. Hicks,
F. Hurtado-Ferro, K.F. Johnson, P.T. Kuriyama, R.R. Licandeo, C.C.
Stawitz, I.G. Taylor, J.L. Valero. The effect of length bin width on
growth estimation in integrated age-structured stock assessments.
Fisheries Research. 180: 103--112.
\url{http://doi.org/10.1016/j.fishres.2015.11.002}
(\href{https://dl.dropboxusercontent.com/u/254940/papers/Monnahan_etal_2016_binwidth.pdf}{PDF}).

@@

of Animal Ecology. 84(3): 840--850.
\url{http://doi.org/10.1111/1365-2656.12322}
(\href{https://dl.dropboxusercontent.com/u/254940/papers/Boudreau_etal_2015_lobster.pdf}{PDF}).

@@

Ecological Applications. 25(2): 559--572.
(\href{https://dl.dropboxusercontent.com/u/254940/papers/Anderson_etal_2015_salmonportfolios.pdf}{PDF}).

@@

Orzechowski, E.A., R. Lockwood, J.E.K. Byrnes, \textbf{S.C. Anderson},
S. Finnegan, Z.V. Finkel, P.G. Harnik, D.R. Lindberg, L.H. Liow, H.K.
interactions over 500 million years. Global Change Biology. 21(10):
3595--3607. \url{http://doi.org/10.1111/gcb.12963}
(\href{https://dl.dropboxusercontent.com/u/254940/papers/Orzechowski_etal_2015_paleometa.pdf}{PDF}).
Finnegan, S., \textbf{S.C. Anderson}, P.G. Harnik, C. Simpson, D.P.

@@

Lockwood, H.K. Lotze, C.R. McClain, J.L. McGuire, A. O'Dea, J.M.

@@

@@

Marine Sciences. 72(1): 99--110.
\url{http://doi.org/10.1093/icesjms/fsu198}
(\href{https://dl.dropboxusercontent.com/u/254940/papers/Hurtado-Ferro_etal_2014_retrospective.pdf}{PDF}).

@@

(\href{http://icesjms.oxfordjournals.org/content/early/2014/04/09/icesjms.fsu055.full.pdf?keytype=ref\&ijkey=NEXmZIkz3289u3z}{PDF}).
Monnahan, C.S. Szuwalski, J.L. Valero, K.A. Vert-Pre, A.R. Whitten, A.E.
age-structured models for marine species. ICES Journal of Marine
Science. 72(1): 31--43. \url{http://doi.org/10.1093/icesjms/fsu007}
(\href{http://icesjms.oxfordjournals.org/content/early/2014/02/20/icesjms.fsu007.full.pdf}{PDF}).

@@

\begin{description}
\itemsep3pt\parskip0pt\parsep0pt
\item[2015]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, M. Dickey-Collas, K.M. Kleisner, C. Longo, G.C.
Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig. Improving
estimates of population status and trend with superensemble models.
American Fisheries Society Annual Meeting, Portland, OR, United States.
\item[2013]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
challenges of quantifying ecological portfolios
(\href{http://seananderson.ca/talks/2013/PE_SAFS_quantsem.pdf}{slides}),
Quantitative Seminar, School of Aquatic and Fishery Sciences, University
of Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. False prophets: The
ecological portfolio effect overestimates the benefit of diversity.
Branch Lab, School of Aquatic and Fishery Sciences, University of
Washington, Seattle, WA, United States.
\item[2012]
\textbf{Anderson, S.C.}, A.B. Cooper, N.K. Dulvy. Metapopulation
dynamics and the generality of the ecological portfolio effect. Les
Ecologistes Departmental Seminar, Simon Fraser University, Burnaby, BC,
Canada.
\item[2010]
\textbf{Anderson, S.C.} The rise of invertebrates, the fall of sea
cucumbers, and the risk of maturing late. Earth2Ocean Research Group,
Simon Fraser University, Burnaby, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E. Mills Flemming, R. Watson, H.K. Lotze.
Ecosystem impacts of the global expansion of invertebrate fisheries.
International Oceans Past II Conference \emph{Multidisciplinary
Perspectives on the History and Future of Marine Animal Populations}.
Vancouver, BC, Canada.
\item[2009]
\textbf{Anderson, S.C.}, J.E Mills Flemming, R. Watson, H.K. Lotze.
Global invertebrate fisheries: trends and consequences. NCEAS (National
Center for Ecological Analysis and Synthesis) Working Group
\emph{Finding Common Ground in Marine Conservation and Management}.
Santa Barbara, CA, USA.
\item[2009]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Harvest Fisheries Seminar Series. Bedford Institute of
Oceanography, Fisheries and Oceans, Dartmouth, NS, Canada.
\item[2008]
\textbf{Anderson, S.C.}, H.K. Lotze, N.L. Shackell. Evaluating the
knowledge base for expanding low-trophic level fisheries in Atlantic
Canada. Departmental Seminar, Biology Department, Dalhousie University,
Canada.
\end{description}

@@

Reviewer for Science, Ecology, Ecological Applications, Conservation
Biology, Fish and Fisheries, International Journal of Tropical Biology
and Conservation, Journal of Environmental Management, Endangered
Species Research, Aquatic Conservation
